\documentclass{article}
\usepackage[utf8]{inputenc}

\title{MHD}
\author{Hannah Gallagher}
\date{December 2021}
\usepackage{amsmath}

\begin{document}

\maketitle


\section{General Relativity Fluids}

Maxwell's equations.


\begin{equation}
    \nabla x \Vec{E}= - \frac{\partial \Vec{B}}{\partial t} \\ 
    \nabla x \Vec{B} = \mu_0 \Vec{J} + \frac{1}{c^2} \frac{\partial \Vec{ E}}{\partial t} \\ 
    \nabla \dot \Vec{E} = \frac{P_0}{\epsilon_0} \\ 
    \nabla \dot \Vec{B} = 0 
\end{equation} 

The simplest idea of how flux and these behave go back to introductory Newtonian physics. 
\\
A perfect fluid for this first iteration example would be one where the viscosity is zero. This is the idea of dry water. 
\begin{equation}
    \left ( \frac{n}{\sqrt{1-v^2}}, \frac{nv^x}{\sqrt{1-v^2}}, \frac{nv^y}{\sqrt{1-v^2}}, \frac{nv^z}{1-v^2}\right) 
\end{equation}
Schutz 
The stress energy tensor helps define these dynamics. 
Conservation of mommentum of particles and geodesics. 

The Bianchi Identities make this achievable. 

As in dynamical systems it all ends in these ten nonlinear coupled differential equations called the Einstein field equations. Understanding this model is essential to a course in general relativity. The importance of shifting from 1d to 2d to 3d to 4d of using spacetime being in constant flux is expanding our knowledge of the universe. 


Magnetohydrodynamics if I were to explain it to someone of my year or age I would say: In the study of magnetic fluids at the end of the day is the direct translation. In terms of what bunch of people that are smarter than me do, they are using these various code packages that all are attempting to do the same thing to simulate how the gases around black holes and other matter behaves. Usually it's written in C++ with some add ons to solve these Einstein field equations in different scenarios of binary neutron star mergers. 

Most of the time they are using numerical methods to solve these problems in the hope that they converge as quickly as possible since this can take years. This theory is in opposition with quantum mechanics, but here at least it deals with differential geometry and how the frame of one's observer can make it seem that the metric is curved or not. 

Similar to how parametric equations and those types of differential models are introduced we continue to expand on these theories with higher complexity and experiments. As with most dynamical systems the fluctuations ebb and flow that these perturbations exist. 




\section{MHD}
APS has physics review D and the fluids section that I've been reading through. \\
I'd have to look back at what I read. There were several problems on Acoustic black holes and how that would be assuming a flat metric. (Paper)



\section{After the semester ended as a sanity check}


\subsection{Meeting with Dr. Campanelli in one hour}
Yes, I am feeling better. I'm embarrassed at how bad my work was and how I forgot the geodesic equation. I subscribed to more of the relevant aps journals. I got too distracted by reading about Optics...at first it was something that I did as a distraction, but now I'm here... I need to own up to not being stupid. I'm not going anywhere. I need to practice my presentations before hand twenty times, but I didn't...I did choke...I was too focused on being impressive I was less focused on the work itself. I've been reviewing my tensor algebra and the einstein field equations...


\subsection{What is she going to say}
You need to do a lot more and maybe this isn't for you... \\ 


First thank her for the course... \\ 

I did learn a lot...just a lot of unexpected things happened. 
I'm getting the booster tomorrow and wasn't feeling well by the end of the semester.

You're asking her for career advice since for a while you've been kind of free wheeling it... I've been subscribed to optics and physics journals for years now. I need to figure out funding, but I'm not leaving the city anytime soon I just signed a lease and still need to finish my last course. My gre physics score did not rank as high as I wanted so I'm taking it again in april. I've never had such a low grade, but I know my health was failing and I was choking more than usual because of how badly I wanted to be impressive. I obviously want to be an author on some things. I need to do the actual work for the statistics they are asking me about. I'm not going anywhere, I just needed a rest. \\ 

I've been desperately working towards understanding the derivations for the Einstein field equations more concretely. \\ 
I have been working on my tensor algebra. \\ 

I think that the covariant derivative is important and the semicolon notation is something that needs practice for me. \\ 

I believe that the paradoxes are important mind exercises. The barn poll examples as well. \\ 


Yes, my work was terrible. It was. I realize that...I feel like I had stroke and my family's health was something that needed more attention than usual. I was distracted by several things and I stopped functioning maybe in November. I wanted to be so impressive that I should have said something about not doing so well... I have significantly a lot of areas in which I need to improve. Giving academic presentations is one of them. 


Slightly grovel for her sticking out her neck for me and then being stupid and lazy. Maybe you'll be able to speak to her if you take the pressure off as if you have another job offer. \\ 

I've been looking at chapter seven all week for forgetting the geodesic equation. I'm worried that you had a bad impression of me being stupid. I read these journals everyday and I've attended all of these colloquiums, but I've been too much of a spectator so I have been making that transition. I do need to figure out funding and applying to grants. I do need to figure out my scholarship situation from sort of having failing health the past few months. There's a lot I need to do in the coming weeks. I've never had a D before. I should know better by now. Normally I can go and knod my head and pretend like I know things then turn around that night and do twelve hours of work to pass off that I know it, but this is one of those situations where that didn't work because of the failing health from me and my family. I feel like I had a stroke from everything that just happened and I just wanted to understand a more complicated version of flux....I do understand up until a certain level. I do not entirely understand the Einstein field equations and that's okay...you'll find funding and it'll be okay. I've been reading more journals on mhd as a sanity check and I was the one who wanted to learn about all of this in the first place...I did get distracted by my optics colleagues...that was my fault. I cared more about authorship than my own course or my family's health and opinions of me...and your opinion of me.

As a sanity check I've been writing a paper to my standards now that I'm feeling better. \\ 

Okay so what exactly happened this semester...anything you wrote was child's play for one thing... I forgot everything...I could barely speak. I think I had some sort of aneurysm. 

I got overzealous about the subject... to do the work itself...this semester was a bust. I got an incomplete in my one course that I'm dealing with next semester and 

\end{document}
